Verifying Demonstrations

### 2018-08-30 paper/timestamp.tex

We need a time-stamping service, \(\TS\), with algorithms \(\TSget\), 
\(\TSstamp\) and \(\TStime\) such that
\begin{itemize}
  \item \(\rho \gets \TSget\) yields a value \(\rho\) at time \(t\), \(\rho\) is difficult to guess before time \(t\) and \(\TStime[\rho] = t\);
  \item \(\pi\gets \TSstamp[x]\) yields a value \(\pi\) at time \(t\) such that 
    \(\TSverify[x, \pi]\to \top\) and \(\TStime[\pi] = t\).
\end{itemize}

With these building blocks we can ensure that a message \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
After time \(t_0\), request \(\rho_{t_0}\gets \TSget\).
Before time \(t_1\), submit \(h\gets \Hash[m, \rho_{t_0}]\) to the time-stamping service to get \(\pi_{t_1}\gets \TSstamp[h]\).

Now we can use \((\rho_{t_0}, m, \pi_{t_1})\) to prove that \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether 
\(\TSverify[h', \pi_{t_1}] = \top\) and \(\TStime[\rho_{t_0}] = t_0\land 
  \TStime[\pi_{t_1}] = t_1\).

We can instantiate \(\TS\) using a distributed ledger, for instance a blockchain instance such as OmniLedger~\cite{OmniLedger}.
The \(\TSstamp[x]\) algorithm will simply include \(x\) in the blockchain and return the identifier of the block into which \(x\) was included.
\(\TSget\) will return the hash of the current head of the chain.
This value is difficult to predict since it depends on all submitted transactions and additional randomness (\eg nonces and miners' secrets).
The blockchain must also be continuously extended, such as in Bitcoin~\cite{Bitcoin}, in which a new block appears approximately every 10 minutes.
%Seb: why is the idea of using a dedicated blockchain not appropriate? we should give more arguments to justify it
Having a dedicated blockchain for a protest is not appropriate, and thus it is better to use a generic blockchain that is used also for other things.

There are some additional properties that we need from \(\TS\), which are implied by blockchains.
First, we need \emph{immutability}, to ensure that once we commit something (through \(\TSstamp\)) it will remain there.
Immutability will also ensure verifiability as the data must remain available to be verifiable.
Second, once we have committed some data, we do not need to keep the data itself, but we can store some confirmation value instead.
For instance in a blockchain, we can store the hash of the block in which our data was committed.
As a consequence, as this block will remain, we are also sure that our data stay committed.\sonja{`` --- even if we no longer remember what our data looked like.'' This was commented out, but the question remains: can we still count?}

>>>>

We need a robust time-stamping service, \(\TS\), which implements the \(\TSget\), 
\(\TSstamp\) and \(\TStime\) requests such that
\begin{itemize}
  \item \(\rho \gets \TSget\) yields a value \(\rho\) at time \(t\), \(\rho\) is difficult to guess before time \(t\) and \(\TStime[\rho] = t\);
  \item \(\pi\gets \TSstamp[x]\) yields a value \(\pi\) at time \(t\) such that 
    \(\TSverify[x, \pi]\to \top\) and \(\TStime[\pi] = t\).
\end{itemize}

With these building blocks we can ensure that a message \(m\) is created within the time interval \(\interval{t_0}{t_1}\).
After time \(t_0\), a user requests \(\rho_{t_0}\gets \TSget\).
Before time \(t_1\), a user submits \(h\gets \Hash[m, \rho_{t_0}]\) to the time-stamping service to get \(\pi_{t_1}\gets \TSstamp[h]\).

The tuple \((\rho_{t_0}, m, \pi_{t_1})\) can be used to prove that \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether 
\(\TSverify[h', \pi_{t_1}] = \top\) and \(\TStime[\rho_{t_0}] = t_0\land 
  \TStime[\pi_{t_1}] = t_1\).

\(\TS\) can be instantiated by an open-membership distributed ledger (\eg a blockchain) such as Bitcoin~\cite{Bitcoin}, secured via Proof-of-Work consensus, or OmniLedger~\cite{OmniLedger}, secured via Byzantine consensus.
If a blockchain is used for \(\TS\), the \(\TSstamp[x]\) request includes \(x\) in the blockchain and returns the identifier of the block into which \(x\) was included.
The \(\TSget\) request returns the hash of the most recent block of the chain (the head).
The returned hash is difficult to predict since it depends on the content of the block, populated by other users and by the creator of the block with additional randomness (\eg nonces and secrets).

Regarding consensus resilience, it is advisable to use a blockchain with a high number of participants even if it means sharing the blockchain with other services.
The resilience of the Byzantine consensus relies on honest participants outnumbering malicious participants.
A similar reasoning can be made with Proof-of-Work consensus where the computing power of the honest participants must outpower the one of malicious participants.
In both cases, assuming a majority of honest members in the population, the more participants the merrier.

We require a few additional properties from \(\TS\) that are already provided by blockchains.
First, \(\TS\) must be continuously extended, such as in Bitcoin where blocks are created every 10 minutes on average.
Second, \(\TS\) must provide \emph{immutability} and availability to any data committed through \(\TSstamp\) to ensure verifiability of the data by anyone at any time.
Once the data from a user is committed, the user can choose to only store some confirmation value instead of the data itself.
In the case of a blockchain, it would be sufficient for a user to only store both the hash of the block containing her proof and the hash of the proof. \sonja{`` --- even if we no longer remember what our data looked like.'' This was commented out, but the question remains: can we still count?}
